### 2024-08-26 paper.tex
move linalg section

\section{Linear Algebra Facts}
In this section we prove linear algebra facts that will be used later.
They are proved in this section to avoid interrupting the flow of the remainder of the paper.

@@

>>>>

@@

\section{Linear Algebra Facts}
In this section we prove linear algebra facts that were used in the paper.
They are confined to this section to avoid interrupting the flow of the paper.
